---
title: "Plotly Graph - Emissions"
author: "Edward Harris"
date: "`r format(Sys.time(), '%d-%B-%Y')`"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(include = FALSE, echo = FALSE, fig.keep = "high")
```

```{r R_packages, results = "hide"}
ipak <- function(pkg){
      new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
      if (length(new.pkg)) 
            install.packages(new.pkg, dependencies = TRUE)
      sapply(pkg, require, character.only = TRUE)
}

# usage
packages <- c("ggplot2", "plyr", "dplyr", "data.table", "reshape2", "RColorBrewer", 
                  "scales", "grid", "shiny", "miniUI", "plotly", "devtools", "htmltools")
ipak(packages)

install_github("plotly", "ropensci", "ropensci/plotly")
```

```{r read_files, results = "hide", cache = TRUE}
#  Read data into R  [assumes files are in working directory]
NEI <- readRDS("summarySCC_PM25.rds")
SCC <- readRDS("Source_Classification_Code.rds")

# Create subset for Southwest Ohio FIPS
SWOH.FIPS <- c("39061", "39025", "39015", "39001",
               "39071", "39027", "39165", "39017",
               "39135", "39113", "39057", "39047")
NEI.SWOH <- subset(NEI, fips %in% SWOH.FIPS)
NEI.SWOH <- unique(NEI.SWOH)
NEI.SWOH <- merge(NEI.SWOH, SCC, by.NEI.SWOH = "SCC", by.SCC = "SCC", all.NEI.SWOH = TRUE)
```

```{r file_smry, results = "hide"}
# Calculate Average / Mean Emissions by year & SCC.Level.One
NEI.SWOH <- select(NEI.SWOH, year, fips, SCC.Level.One, Emissions)
NEI.SWOH$SCC.Level.One <- as.character(NEI.SWOH$SCC.Level.One)
NEIagg <- aggregate(Emissions ~ year + SCC.Level.One, data = NEI.SWOH, FUN = mean)
```

<p style="page-break-before: always">
## Emissions Data in the United States
In the Data Science Specialtization: Course 4 Exploratory Data Analysis, we explored the National Emissions Inventory database and see what it says about fine particulate matter pollution in the United States over the 10-year period 1999–2008.  The data provided by instructors was contained in two data sets, then a subset is used:  
1. PM2.5 Emiisions Data (summarySCC_PM25.rds) is a data frame that contains all of the PM2.5 emissions data for 1999, 2002, 2005, and 2008.    
2. Sourece Classification Code Table (Source_Classification_Code.rds) provides a mapping from the SCC digit strings in the Emissions table to the actual name of the PM2.5 source.  
3. Subset for 12 southwest Ohio counties defined using fips.    
---

<p style="page-break-before: always">
```{r create_plot, fig.align = 'center', fig.heigth = 5, fig.width = 5, fig.keep ='high'}
g <- ggplot(NEIagg, aes(x = year, y = Emissions, color = SCC.Level.One)) +
     geom_point() +
     geom_line(aes(group = SCC.Level.One))

gg <- ggplotly(g)

plotly_POST(gg)

# ui <- fluidPage(
#      plotlyOutput("plot"),
#      verbatimTextOutput("Southern Ohio Emissions")
# )

# server <- function(input, output) {
#      output$plot <- renderPlotly({
#            plot_ly(NEIagg, x = ~year, y = ~Emissions, color = ~SCC.Level.One,
#            type = 'scatter', mode = 'lines+markers')
#      })
#      output$event <- renderPrint({
#            d <- event_data("plotly_hover")
#            if(is.null(d)) "Hover on a point!" else d
#      })
# }

# shinyApp(ui, server)



# p <- plot_ly(NEIagg, x = ~year, y = ~Emissions, color = ~SCC.Level.One,
#              type = 'scatter', mode = 'lines+markers') %>%
#       layout(
#             title = "Southwest Ohio Emission Levels",
#             scene = list(
#                   xaxis = list(title = "Measurement Year"),
#                   yaxis = list(title = "Avg Emissions")
#             ))

# plotly_POST(p, filename = "r-docs/emissions-linegraphs")

## iframe src="https://plot.ly/~RPlotBot/501.embed"
##         height="600" width="100%"
##         scrolling="no" seamless="seamless"
##         frameBorder="0"
## </iframe>


#htmltools::includeHTML("p.html")

```
---




